The Spine of American Legal Practice

### 2016-06-28 article/article.Rmd
Standardize labels and legend sizes

---
author:
- Kellen Funk
- Lincoln Mullen
fontsize: 12pt
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
title: The Spine of American Legal Practice
---

@@

```{r ca1850-borrowings, fig.height=3, fig.align="center"}
spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
                                                   "NY1848"))
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
spectrogram("CA1851", best_matches, white_list = 3)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
                                                   "NY1853", "OR1854", "WI1849"))
```

@@

```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1873", best_matches)
```

@@

Uniformity in the law, as shown through these clusters, is just as instructive as variation. The most significant clusters that we investigated related to the collection of debts. These were clusters which went against the typical pattern we observed. While most clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South. No single section of the code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections. In New York's original enacted code from 1848, §107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); §202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§128--133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution. These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years. The Field code's summary judgment brought down the time of debt collection to a matter of weeks. Effectively, the code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]

@@

[^36]: We filtered this matrix based on what we knew about the process of borrowing. We removed any match below a threshold that we determined by reading pairs of matches. Because Jaccard similarity scores are symmetric, we also removed anachronistic matches. For instance, a code from 1851 obviously did not borrow from a code from 1877. Furthermore, in chains of borrowing (e.g., NY1850 → CA1851 → CA1868 → CA1872 → MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent. We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold. Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.

@@

[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999) : 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.

>>>>

---
author:
- Kellen Funk
- Lincoln Mullen
fontsize: 12pt
fontfamily: 
  - mathpazo
output:
  pdf_document:
    fig_caption: True
    md_extensions: '-tex_math_single_backslash'
    number_sections: False
title: The Spine of American Legal Practice
---

@@

```{r ca1850-borrowings, fig.height=3, fig.align="center"}
spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
                                                   "NY1848"),
            base_size = 10)
```

@@

```{r CA1851-borrowings, fig.height=3.5, fig.align="center"}
spectrogram("CA1851", best_matches, white_list = 3,
            base_size = 10)
```

@@

```{r WA1855-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
                                                   "NY1853", "OR1854", "WI1849"),
            base_size = 10)
```

@@

```{r WA1873-borrowings, fig.height=4.5, fig.align="center"}
spectrogram("WA1873", best_matches,
            base_size = 10)
```

@@

Uniformity in the law, as shown through these clusters, is just as instructive as variation. The most significant clusters that we investigated related to the collection of debts. These were clusters which went against the typical pattern we observed. While most clusters exhibited regional variation as they grew more distant from the Field Code, clusters having to do with creditors' remedies were almost completely uniform across the American West and South. No single section of the code announced its preference for creditors' rights; rather, the acceleration of creditors' remedies resulted from the combination of several sections. In New York's original enacted code from 1848, §107 required a defendant to answer the complaint within twenty days, instead of at the next court session (which in some cases could have been as far as three months away); §202 provided for default judgment as a matter of course, issued by a clerk without a judicial order if no adequate answer was received within the twenty days; §§128--133 abolished fictitious pleadings and required answers to state true facts verified by a defendant's oath, all so that no trial would delay the enforcement of uncontestable obligations; finally, the code abolished a traditional thirty-day waiting period between issue of judgment and commencement of execution. These provisions dealt with what merchants and capitalists perceived as an abuse of the common law system, where defendants in cases of debt could stretch out enforcement of debt collection for as long as two years. The Field code's summary judgment brought down the time of debt collection to a matter of weeks. The code traded the rhythms of agriculture for the rhythms of merchant finance.[^48]

@@

[^36]: We filtered this matrix based on what we knew about the process of borrowing. We removed any match below a threshold that we determined by reading pairs of matches. Because Jaccard similarity scores are symmetric, we also removed anachronistic matches. For instance, a code from 1851 obviously did not borrow from a code from 1877. Furthermore, in chains of borrowing (e.g., NY1850 to CA1851 to CA1868 to CA1872 to MT1895) the latest section might have a high similarity to all of its ancestors, but it was in fact borrowed only from the most recent parent. We therefore filtered the similarity matrix to remove matches within the same code; anachronistic matches; spurious matches beneath a certain threshold. Then if a section had multiple matches, we kept the match from the chronologically closest code, giving preference to codes from the same state, unless there was a substantially closer match from a different code.

@@

[^47]: Samuels, Lisa, and Jerome McGann. "Deformance and Interpretation." *New Literary History* 30.1 (1999): 25--56; Mark Sample, "Notes toward a Deformed Humanities," blog post, 2 May 2012: <http://www.samplereality.com/2012/05/02/notes-towards-a-deformed-humanities/>; Ramsay, *Reading Machines*, 32--57.
